---
title: "results"
author: "Keana Richards"
date: "6/10/2020"
output:
  bookdown::word_document2:
  fig_caption: yes 
---

```{r, include = F}

## hiding code chunks globally 
knitr::opts_chunk$set(echo=F, message = F, warning = F)


## limiting number of digits to 2 decimal places
options(digits = 2)
options(repos="https://cran.rstudio.com" )
# load packages -----------------------------------------------------------


## Install devtools package if necessary
if(!"devtools" %in% rownames(installed.packages())) install.packages("devtools")


## Package names
packages <- c("readr", "tidyverse", "here", "devtools", "knitr", "officer", "summarytools")

## Install packages not yet installed
installed_packages <- packages %in% rownames(installed.packages())
if (any(installed_packages == FALSE)) {
  install.packages(packages[!installed_packages])
}

## Packages loading
invisible(lapply(packages, library, character.only = TRUE))

## Install the stable development versions from GitHub
if(!"papaja" %in% rownames(installed.packages())) devtools::install_github("crsh/papaja")

library(papaja)

source(here("study2", "source", "01_preregistered-analyses.R"))
source(here("study2", "source", "03_exploratory-analyses.R"))


na_drop <- clean %>% drop_na(condition) 

```

```{r, results = "asis"}
## print(ctable(na_drop$gender, na_drop$condition))
```

We replicated the effect of gender on the choice to compete when gender is included as the only predictor in the logistic regression: `r ctable(clean$gender, clean$comp_choice, useNA = "no")$proportions[4]*100`% of men chose to compete compared to `r ctable(clean$gender, clean$comp_choice, useNA = "no")$proportions[5]*100`% of women, `r apa_print(sec_exploratory7)$full_result$genderWoman`. Like Study 1, the gender effect on competitiveness is no longer significant after adding the same control variables as before (i.e., risk attitudes, confidence, task scores, and the hypothesized interaction between gender and condition), where risk attitudes, `r apa_print(exploratory1)$full_result$risk`, confidence, `r apa_print(exploratory1)$full_result$conf_rank`, and task scores, `r apa_print(exploratory1)$full_result$task_score` appear to explain the gender differences in competitiveness. Again, we find that gender predicts task scores when included by itself as a predictor, `r apa_print(exploratory4)$full_result$genderWoman`. However, unlike Study 1, when other variables are included as predictors in the linear regression, we find that the effect of gender on task scores dissipates, `r apa_print(sec_exploratory10)$full_result$genderWoman`, suggesting that the other variables, such as risk attitudes, `r apa_print(sec_exploratory10)$full_result$risk`, and confidence, `r apa_print(sec_exploratory10)$full_result$conf_rank`, explained the gender difference in task scores in this study. In support of this possibility, we replicate the finding from the Study 1 of this chapter that gender predicts both risk attitudes, `r apa_print(sec_exploratory8)$full_result$risk`, and confidence, `r apa_print(sec_exploratory9)$full_result$conf_rank`. 


We did not find evidence of an interaction between gender and condition on the choice to compete in a logistic regression, `r apa_print(sec_exploratory14)$full_result$genderWoman_conditionpract` (see Figure \@ref(fig:s200)). Also, we do not find evidence of a significant effect of condition on the choice to compete as a sole predictor in a logistic regression, `r apa_print(exploratory5)$full_result$conditionpract`.



```{r, results = "asis"}
woman <- clean %>% filter(gender == "Woman")
## print(ctable(woman$comp_choice, woman$condition))

```

Despite no evidence for the effect of condition on the choice to compete across participants, we replicate the effect of gender on the choice to practice found in Study 1, where women were significantly more likely to prepare for the task, even after being forced to prepare in the preparation condition (see Figure \@ref(fig:s204)). `r ctable(clean$gender, clean$pract_choice, useNA = "no")$proportions[5]*100`% of women across conditions chose to practice for the multiplication task, relative to `r ctable(clean$gender, clean$pract_choice, useNA = "no")$proportions[4]*100`%% of men, `r apa_print(sec_exploratory16)$full_result$genderWoman` (see Figure \@ref(fig:s207)). The gender effect holds even after controlling for the decision to compete and the interaction between gender and the decision to compete, `r apa_print(sec_exploratory11)$full_result$genderWoman` (see Figure \@ref(fig:s201)). Within the same model, we find that the choice to compete itself increases the likelihood a participant will practice before completing the paid task, `r apa_print(sec_exploratory11)$full_result$comp_choicetournament`, but no evidence of an interaction between gender and payment scheme choice, `r apa_print(sec_exploratory11)$full_result$genderWoman_comp_choicetournament`. To see if the gender effect is explained by other variables included in the study, we added confidence, risk attitudes, and task scores to the previous model, and find that gender still significantly predicts the choice to practice, `r apa_print(sec_exploratory13)$full_result$genderWoman`, over any effects of differences in risk attitudes, confidence, or task scores.^[Note: We ran the same two-part hurdle model described in Study 1 with gender, competition choice, and the interaction between those variables predicting the number of practice rounds variable. Again, we do not find evidence of gender differences in the choice to continue preparing after the initial decision to prepare].   


Again, we find that these results align with participants' expectations, where they were significantly more likely to expect women (with `r unname(prop.table(t3)*100)[2]`% selecting women versus `r unname(prop.table(t3)*100)[1]`% selecting men) to choose to prepare more than men both in general, `r apa_print(exploratory3c, n = nrow(clean))$statistic` (see Figure \@ref(fig:s206)), and on the paid multiplication task, `r apa_print(exploratory3d, n = nrow(clean))$statistic` (see Figure \@ref(fig:s203)) (with `r unname(prop.table(t4)*100)[2]`% selecting women versus `r unname(prop.table(t4)*100)[1]`% selecting men), despite expecting men to choose to compete more often, `r apa_print(exploratory3b, n = nrow(clean))$statistic` (see Figure \@ref(fig:s205)) and expecting no gender differences in performance on the task, `r apa_print(exploratory3a, n = nrow(clean))$statistic` (see Figure \@ref(fig:s204)). 

We also added several post-manipulation questions to tap into participants' experience of the multiplication task itself, feelings of preparedness, and general beliefs about the value of preparation to see if they may explain some of the observed effects. First, in a logistic regression with preparedness regressed upon condition and the interaction between preparation choice and gender, only the choice to prepare predicts feelings of preparation, `r apa_print(sec_exploratory19)$full_result$pract_choiceYes`. However, we do not have evidence that gender predicts field-specific ability beliefs, `r apa_print(sec_exploratory20)$full_result$genderWoman`, contrary to previous literature (INSERT confirm if this is correct). 

We also tested whether the interaction between practice choice and condition, along with gender, predict participants' interest in the multiplication and self-reported fatigue after completing the paid task. Our results suggest that participants who chose to prepare before the task reported feeling significantly more fatigued than those who did not choose to practice, `r apa_print(sec_exploratory18)$full_result$pract_choiceYes`, and that participants in the preparation condition were significantly more fatigued than those who were assigned to the control condition, `r apa_print(sec_exploratory18)$full_result$conditionpract`. We do not find evidence that gender, `r apa_print(sec_exploratory18)$full_result$genderWoman`, nor the interaction between condition and practice choice, `r apa_print(sec_exploratory18)$full_result$pract_choiceYes_conditionpract`, predicted self-reported fatigue. Finally, we find that women report being significantly less interested in the task, `r apa_print(sec_exploratory21)$full_result$genderWoman`, even though participants who chose to prepare tend to be significantly more interested in the task, `r apa_print(sec_exploratory21)$full_result$pract_choiceYes`. No other effects in the model are significant. 

```{r, results = "asis"}
## print(ctable(clean$gender, clean$better_gender_guess))
```


```{r, results = "asis"}
## print(ctable(clean$gender, clean$perc_gender_comp))
```



```{r, results = "asis"}
## print(ctable(clean$gender, clean$perc_gen_gender_pract))
```


