---
title: "results"
author: "Keana Richards"
date: "6/10/2020"
output:
  bookdown::word_document2:
  fig_caption: yes 
---

```{r, include = F}

## hiding code chunks globally 
knitr::opts_chunk$set(echo=F, message = F, warning = F)


## limiting number of digits to 2 decimal places
options(digits = 2)
options(repos="https://cran.rstudio.com" )
# load packages -----------------------------------------------------------


## Install devtools package if necessary
if(!"devtools" %in% rownames(installed.packages())) install.packages("devtools")


## Package names
packages <- c("readr", "tidyverse", "here", "devtools", "knitr", "officer", "summarytools")

## Install packages not yet installed
installed_packages <- packages %in% rownames(installed.packages())
if (any(installed_packages == FALSE)) {
  install.packages(packages[!installed_packages])
}

## Packages loading
invisible(lapply(packages, library, character.only = TRUE))

## Install the stable development versions from GitHub
if(!"papaja" %in% rownames(installed.packages())) devtools::install_github("crsh/papaja")

library(papaja)

source(here("study2", "source", "01_preregistered-analyses.R"))
source(here("study2", "source", "03_exploratory-analyses.R"))


na_drop <- clean %>% drop_na(condition) 

```

```{r, results = "asis"}
## print(ctable(na_drop$gender, na_drop$condition))
```

We replicated the effect of gender on the choice to compete when gender is included as the only predictor in the logistic regression: `r ctable(clean$gender, clean$comp_choice)$proportions[4]*100`% of men chose to compete compared to `r ctable(clean$gender, clean$comp_choice)$proportions[5]*100`% of women, `r apa_print(sec_exploratory7)$full_result$genderWoman`. Like Study 1, the gender effect on competitiveness is no longer significant after adding the same control variables as before (i.e., risk attitudes, confidence, task scores, and the hypothesized interaction between gender and condition), where risk attitudes, `r apa_print(exploratory1)$full_result$risk`, confidence, `r apa_print(exploratory1)$full_result$conf_rank`, and task scores, `r apa_print(exploratory1)$full_result$task_score` appear to explain the gender differences in competitiveness. Again, we find that gender predicts task scores when included by itself as a predictor, `r apa_print(exploratory4)$full_result$genderWoman`. However, when other variables are included as predictors in the linear regression, we find that the effect of gender on task scores dissipates, `r apa_print(sec_exploratory10)$full_result$genderWoman`, suggesting that the other variables, such as risk attitudes, `r apa_print(sec_exploratory10)$full_result$risk`, and confidence, `r apa_print(sec_exploratory10)$full_result$conf_rank`, explained the gender difference in task scores in this study. In support of this possibility, we replicate the finding from the Study 1 of this chapter that gender predicts both risk attitudes, `r apa_print(sec_exploratory8)$full_result$risk`, and confidence, `r apa_print(sec_exploratory9)$full_result$conf_rank`. 


We did not find evidence of an interaction between gender and condition on the choice to compete in a logistic regression, `r apa_print(sec_exploratory14)$full_result$genderWoman_conditionpract` (see Figure \@ref(INSERT)). Also, we do not find evidence of a significant effect of condition on the choice to compete as a sole predictor in a logistic regression, `r apa_print(exploratory5)$full_result$conditionpract`.



```{r, results = "asis"}
woman <- clean %>% filter(gender == "Woman")
## print(ctable(woman$comp_choice, woman$condition))

```

Despite no evidence for the effect of condition (whether they completed relevant preparation or irrelevant preparation) on the choice to compete across participants, we replicate the effect of gender on the choice to practice found in Study 1, where women were significantly more likely to prepare for the task, even after being forced to prepare in the preparation condition (see Figure \@ref(fig:s204)). INSERT% of women across conditions chose to practice for the multiplication task, relative to X% of men, `r apa_print(sec_exploratory16)$full_result$genderWoman`. The gender effect holds even after controlling for the decision to compete and the interaction between gender and the decision to compete, `r apa_print(sec_exploratory11)$full_result$genderWoman` (see Figure \@ref(fig:s204)). Within the same model, we find that the choice to compete itself increases the likelihood a participant will practice before completing the paid task, `r apa_print(sec_exploratory11)$full_result$comp_choicetournament`, but no evidence of an interaction between gender and payment scheme choice, `r apa_print(sec_exploratory11)$full_result$genderWoman_comp_choicetournament`. To see if the gender effect is explained by other variables included in the study, we added confidence, risk attitudes, and task scores to the previous model, and find that gender still significantly predicts the choice to practice, `r apa_print(sec_exploratory13)$full_result$genderWoman`, over any effects of differences in risk attitudes, confidence, or task scores.  
INSERT summary for practice count var: `r apa_print(sec_exploratory12)$full_result$genderWoman`


Again, we find that these results align with participants' expectations, where they were significantly more likely to expect women to choose to prepare more than men both in general, `r apa_print(exploratory3c, n = nrow(clean))$statistic`, and on the paid multiplication task, `r apa_print(exploratory3d, n = nrow(clean))$statistic` (see Figure \@ref(fig:s203)), despite expecting men to choose to compete more often, `r apa_print(exploratory3b, n = nrow(clean))$statistic` (see Figure \@ref(fig:s202)) and expecting no gender differences in performance on the task, `r apa_print(exploratory3a, n = nrow(clean))$statistic` (see Figure \@ref(fig:s201)). 

```{r, results = "asis"}
## print(ctable(clean$gender, clean$better_gender_guess))
```


```{r, results = "asis"}
## print(ctable(clean$gender, clean$perc_gender_comp))
```



```{r, results = "asis"}
## print(ctable(clean$gender, clean$perc_gen_gender_pract))
```


