---
title: "summary of main results across dissertation studies"
author: "Keana Richards"
output:
  html_document:
    chunk_output_type: console
    number_sections: yes
    theme: cerulean
    toc: yes
    toc_depth: 4
    toc_float: yes
  pdf_document:
    toc: yes
    toc_depth: '4'
editor_options: 
  chunk_output_type: console
---


- [Table showing analyses run across studies](https://www.notion.so/8fd828e48c6141d8be7173e7dc16c201?v=74078e30124e47289cc447b01a760617) 

# Study 1.1 

```{r, include = F}
knitr::opts_chunk$set(echo = FALSE, message=FALSE, warning = F)


## limiting number of digits to 2 decimal places
options(digits = 2)
options(repos="https://cran.rstudio.com" )

# load packages -----------------------------------------------------------

if(!require('pacman')) {
  install.packages('pacman')
  }
pacman::p_load(tidyverse, here, hablar, psych, qualtRics, summarytools, varhandle, sjPlot, papaja, gtsummary, report)


source(here("study1", "source", "01_preregistered-analyses.R"))
source(here("study1", "source", "03_exploratory-analyses.R"))


## Install the stable development versions from GitHub
# if(!"papaja" %in% rownames(installed.packages())) devtools::install_github("crsh/papaja")
# if(!"emo" %in% rownames(installed.packages())) devtools::install_github("hadley/emo")
# library(emo)
# library(papaja)


# na_drop <- clean %>% drop_na(condition) 
extrafont::loadfonts(device="win")


options(scipen=999)
par(mar = c(2,2,2,2))


```


## Main analyses to be included 


```{r}

## need to run chi square tests individually 

exploratory7d
 exploratory7c
 exploratory7b
 exploratory7a
 

models_study1b <- list(sec_exploratory7,
                     sec_exploratory8,
                     sec_exploratory9,
                     sec_exploratory12, 
                     sec_exploratory2,
                     sec_exploratory13,
                     sec_exploratory14,
                     sec_exploratory6,
                     sec_exploratory11,
                     primary_hyp1,
                     sec_exploratory15
 )

map(models_study1b, report)



```



## Dataset summary (overall)

```{r}
# clean %>%  tbl_summary()

```

## Dataset summary (by gender)

```{r}
## see Penn -> cnl -> narratives -> demographics_table_study1.R & 
## https://www.danieldsjoberg.com/gtsummary/articles/tbl_summary.html for inspo

# clean %>%  tbl_summary(by = gender)



```


# Study 1.2


```{r}
source(here("study2", "source", "01_preregistered-analyses.R"))
source(here("study2", "source", "03_exploratory-analyses.R"))

```


## Main analyses to be included 


```{r}

## need to run chi square tests individually 


exploratory3d
 exploratory3c
 exploratory3b
 exploratory3a

models_study2b <- list( sec_exploratory8,
 sec_exploratory9,
 exploratory4,
 sec_exploratory10,
 sec_exploratory11,
 sec_exploratory12,
 sec_exploratory13,
 sec_exploratory7,
 exploratory1,
 sec_exploratory14,
 exploratory5
 )

map(models_study2b, report)



```



## Dataset summary (overall)

```{r}
# clean %>%  tbl_summary()

```

## Dataset summary (by gender)

```{r}
## see Penn -> cnl -> narratives -> demographics_table_study1.R & 
## https://www.danieldsjoberg.com/gtsummary/articles/tbl_summary.html for inspo

# clean %>%  tbl_summary(by = gender)



```



# Study 1.3

```{r}
source(here("study4", "source", "01_preregistered-analyses.R"))
source(here("study4", "source", "03_exploratory-analyses.R"))

```

## Main analyses to be included 

```{r}

## need to run chi square tests individually 

exploratory7
 exploratory6
 exploratory5
 exploratory4
exploratory30
exploratory31
exploratory32
exploratory33
exploratory34
exploratory35
 exploratory36
 exploratory37
 

models_study3b <- list( exploratory17,
 exploratory18,
 exploratory19,
 exploratory20,
 exploratory3,
 exploratory28,
 exploratory29,
 exploratory16,
 hypothesis3c,
 hypothesis3a,
 exploratory22
 )

map(models_study3b, report)



```


## Dataset summary (overall)

```{r}
# clean_fraud_removed %>%  tbl_summary()

```

## Dataset summary (by gender)

```{r}
## see Penn -> cnl -> narratives -> demographics_table_study1.R & 
## https://www.danieldsjoberg.com/gtsummary/articles/tbl_summary.html for inspo

# clean_fraud_removed %>%  tbl_summary(by = gender)



```



# Study 2.1 

```{r}
source(here("study5", "source", "01_preregistered-analyses.R"))
source(here("study5", "source", "03_exploratory-analyses.R"))

```

## Main analyses to be included 

```{r}

## need to run chi square tests individually 

sec_exploratory3b
sec_exploratory3e
 sec_exploratory3c 
 sec_exploratory3d
 sec_exploratory3a
sec_exploratory14
sec_exploratory15
sec_exploratory16
sec_exploratory17
sec_exploratory18
sec_exploratory19
sec_exploratory20
sec_exploratory21
sec_exploratory22
sec_exploratory23


models_study4b <- list( sec_exploratory7,
 sec_exploratory8,
 sec_exploratory12,
 sec_exploratory4,
 hypothesis1,
 exploratory4b,
 sec_exploratory13
 )

map(models_study4b, report)



```

## Dataset summary (overall)

```{r}
# clean_fraud_removed %>%  tbl_summary()

```

## Dataset summary (by gender)

```{r}
## see Penn -> cnl -> narratives -> demographics_table_study1.R & 
## https://www.danieldsjoberg.com/gtsummary/articles/tbl_summary.html for inspo

# clean_fraud_removed %>%  tbl_summary(by = gender)



```




