---
title: "results"
author: "Keana Richards"
output:
  bookdown::word_document2:
  fig_caption: yes 
---

```{r, include = F}

## hiding code chunks globally 
knitr::opts_chunk$set(echo=F, message = F, warning = F)


## limiting number of digits to 2 decimal places
options(digits = 2)
options(repos="https://cran.rstudio.com" )
# load packages -----------------------------------------------------------


## Install devtools package if necessary
if(!"devtools" %in% rownames(installed.packages())) install.packages("devtools")


## Package names
packages <- c("readr", "tidyverse", "here", "devtools", "knitr", "officer", "summarytools", "conflicted")

## Install packages not yet installed
installed_packages <- packages %in% rownames(installed.packages())
if (any(installed_packages == FALSE)) {
  install.packages(packages[!installed_packages])
}

## Packages loading
invisible(lapply(packages, library, character.only = TRUE))

## Install the stable development versions from GitHub
if(!"papaja" %in% rownames(installed.packages())) devtools::install_github("crsh/papaja")

library(papaja)

conflict_prefer("select", "dplyr")
conflict_prefer("filter", "dplyr")

source(here("study4", "source", "01_preregistered-analyses.R"))
source(here("study4", "source", "03_exploratory-analyses.R"))


na_drop <- clean %>% drop_na(condition) 
practice <- clean %>% filter(condition == "pract")
woman <- clean %>% filter(gender == "Woman")

```

## Contrasting results with previously found effects - gender effects on risk attitudes, confidence, choice to compete, and performance 

We start by exploring gender differences across the main variables of interest to compare the characteristics of our sample to previous samples and provide context for the subsequent analyses. First, we replicated the effect from the previous studies of gender on the choice to compete when gender is included as the only predictor in the logistic regression: `r ctable(clean_fraud_removed$gender, clean_fraud_removed$comp_choice)$proportions[4]*100`% of men chose to compete compared to `r ctable(clean_fraud_removed$gender, clean_fraud_removed$comp_choice)$proportions[5]*100`% of women, `r apa_print(exploratory16)$full_result$genderWoman`. However, like the previous two studies, when running regressions including control variables (i.e., task score, risk attitudes, confidence, and the interaction between gender and condition), we find that the effect of gender on the choice to compete is not significant, `r apa_print(hypothesis3c)$full_result$genderWoman`, suggesting the effect is explained fully by risk attitudes, `r apa_print(hypothesis3c)$full_result$risk`, task score, `r apa_print(hypothesis3c)$full_result$task_score`, and confidence, `r apa_print(hypothesis3c)$full_result$conf_rank`. 

On the other hand, we replicate effects from the literature of gender on both confidence, `r apa_print(exploratory18)$full_result$genderWoman`, and risk attitudes, `r apa_print(exploratory17)$full_result$genderWoman`, where women tend to be less confident with regards to their performance on the task and generally more risk averse relative to men.

Another important consideration when interpreting any main effects found in this study is whether there are gender differences in task scores. If there are differences in task scores, it may explain any observed differences in the choice to prepare and the perceived benefits of the preparation condition overall. When including gender by itself as a predictor of performance, we find that women have significantly lower task scores, `r apa_print(exploratory19)$full_result$genderWoman`. However, when controlling for confidence and risk attitudes, the effect of gender is not significant, `r apa_print(exploratory20)$full_result$genderWoman`, suggesting that these variables explain the gender difference in task scores. Specifically, we find that confidence positively predicts task scores (that is, those who are more confident tend to have higher task scores), `r apa_print(exploratory20)$full_result$conf_rank`, while risk attitudes negatively predict task scores (that is, individuals who are more risk seeking tend to have lower scores), `r apa_print(exploratory20)$full_result$risk`.


## Main effects of condition on choice to compete & related exploratory analyses 

We do not find evidence of a significant effect of condition on the choice to compete across all participants, `r apa_print(exploratory22)$full_result$conditionpract` when included as a single predictor of the choice to compete in a logistic regression. In a subsequent logistic regression adding in gender and the interaction between gender and condition as predictors, we find that gender is the only significant predictor of the choice to compete, `r apa_print(hypothesis3a)$full_result$genderWoman` and no evidence of the expected interaction effect between gender and condition on the choice to compete, `r apa_print(hypothesis3a)$full_result$genderWoman_conditionpract` (see Figure \@ref(fig:s301)). 

## Validating the perceived utility of preparation condition over control condition

Since we did not find any effect of condition and this study uses a novel control task that has not been used in previous studies, we ran some analyses to test whether participants actually felt like the preparation condition was more useful for performance on the paid multiplication task than the control condition. It is possible we did not observe an effect of condition on the choice to compete, nor an interaction effect between gender and condition, because participants simply did not think the preparation task would be more helpful for improving their performance relative to the control condition. 

To explore this null effect further, we looked into how much participants were choosing to practice across conditions, which may provide insight into why there was no difference in the choice to compete across conditions. It is possible that participants in the control condition decided to complete subtraction problems at similar rates as participants in the preparation condition, and if so, this may have led them to compete at similar rates because the subtraction tables felt easier than the multiplication tables, and therefore boosted their confidence or reduced perceptions of risk. Contrary to this possibility, we find that participants in the practice condition tended to choose to study, INSERT MODEL (need to run), and practice, INSERT MODEL (need to run), the multiplication tables at significantly higher rates relative to participants in the control condition. 

In further evidence of the perceived utility of the preparation condition for improving performance on the paid multiplication task, participants across both conditions tended to believe when asked in the manipulation check that practicing multiplication problems would be more likely to improve performance on the paid multiplication task than practicing subtraction problems, INSERT MODEL. 

```{r}
# print(stby(list(women$condition,women$practice_problems_binary), INDICES = women$comp_choice, FUN = ctable))
# print(stby(list(women$condition,women$study_tables_binary), INDICES = women$comp_choice, FUN = ctable))

```

## Gender differences in the decision to practice 

Our next set of analyses focused on the effects of gender on decisions to prepare. Thus, all subsequent analyses focus on the subset of participants that were assigned to the unlimited preparation condition that were actually given the opportunity to practice beforehand (N = `r nrow(practice)`). 

We do not replicate the effect found in both previous studies of gender on the decision to practice multiplication problems, neither in the model where gender is included by itself as a sole predictor of the choice to practice, `r apa_print(sec_exploratory39)$full_result$genderWoman`, nor in tandem with the choice to compete and the interaction between gender and the choice to compete as predictors, `r apa_print(exploratory3)$full_result$genderWoman`. In line with the previous studies, we do not find an interaction between gender and choice to compete on the choice to practice, `r apa_print(exploratory3)$full_result$genderWoman_comp_choicetournament`; instead we find that, like previous studies, the choice to compete is positively related to the choice to practice, `r apa_print(exploratory3)$full_result$comp_choicetournament`. In adding confidence and risk attitudes as predictors to the model with the interaction effect on top of the main effects, we do not find evidence that either of those predictors are significantly related to the choice to practice either. 

Finally, we tested whether the number of extra practice rounds completed differed across genders, and unlike previous studies, did not find evidence for this hypothesis, `r apa_print(exploratory28)$full_result$genderWoman`. Unlike the previous studies, this study separated the decision to study tables and amount of time studying tables from the decision to practice and number of problems completed, so we had the novel opportunity to explore questions about gender differences in studying here. Though we do not find evidence that there are gender differences in the decision to study the multiplication tables, INSERT MODEL, among those who did choose to study (N = `r nrow(practice %>% filter(study_tables_binary == "Yes"))`; `r nrow(practice %>% filter(study_tables_binary == "Yes"))/nrow(practice)*100`% of participants in the preparation condition), we find that women studied for INSERT seconds longer than men on average, Mwomen=INSERT, SD=INSERT; Mmen=INSERT, sd=INSERT, INSERT MODEL.   

## Perceptions of gender differences in performance, competition, and preparation

Like all studies before, for each question about perceptions of gender differences, we run a chi-square goodness of fit test with the null hypothesis that participants' will choose each option at a similar rate. Since participants were given the option in this study to select one of three response options, rather than two options like the first two studies, we first perform a chi-square goodness of fit test with all response options to see if they are all equally likely. If the test with all three response options was significant, we then performed more targeted chi-square goodness of fit test with pairs of response options within a given question to test which specific pairs of response options are significantly different.    

When asked to predict gender differences in preparation for the multiplication task (among participants in the preparation condition), we find that participants' responding is not evenly distributed across the response options, `r apa_print(exploratory7, n = nrow(clean_fraud_removed))$statistic`. In performing more targeted analyses, we find that participants were significantly more likely to choose “women” (`r unname(prop.table(t4)*100)[3]`%) than “men” (`r unname(prop.table(t4)*100)[1]`%), `r apa_print(exploratory33, n = nrow(clean_fraud_removed))$statistic`, or “no difference” (`r unname(prop.table(t4)*100)[2]`%), `r apa_print(exploratory32, n = nrow(clean_fraud_removed))$statistic`, when asked about gender differences in tendencies to prepare on the multiplication task.

This result replicates when participants are asked about gender differences in general tendencies to prepare, `r apa_print(exploratory6, n = nrow(clean_fraud_removed))$statistic`, such that, across all participants, a significantly higher proportion of participants said women prepare more in general (`r unname(prop.table(t3)*100)[3]`%) than the proportion of participants that said men prepare more (`r unname(prop.table(t3)*100)[1]`%), `r apa_print(exploratory35, n = nrow(clean_fraud_removed))$statistic`, or there are no gender differences in general tendencies to prepare (`r unname(prop.table(t3)*100)[2]`%), `r apa_print(exploratory34, n = nrow(clean_fraud_removed))$statistic`. 

Though participants consistently expected women to be more likely to prepare than men, they did not expect that there would be a gender difference in performance, `r apa_print(exploratory4, n = nrow(clean_fraud_removed))$statistic`, where participants were significantly more likely to indicate "no difference" (`r unname(prop.table(t1)*100)[2]`%), `r apa_print(exploratory4, n = nrow(clean_fraud_removed))$statistic`, compared to "men" (`r unname(prop.table(t1)*100)[1]`%), `r apa_print(exploratory30, n = nrow(clean_fraud_removed))$statistic`, or "women" (`r unname(prop.table(t1)*100)[3]`%), `r apa_print(exploratory31, n = nrow(clean_fraud_removed))$statistic`, when asked if they thought men or women correctly solved more multiplication problems on average. 


Despite thinking that there would be no gender difference in performance and expecting women to prepare for the task more, participants consistently expected men to be more likely to compete (`r unname(prop.table(t2)*100)[1]`%), `r apa_print(exploratory5, n = nrow(clean_fraud_removed))$statistic`, rather than expecting women to compete more (`r unname(prop.table(t2)*100)[3]`%), `r apa_print(exploratory37, n = nrow(clean_fraud_removed))$statistic`, or expecting no difference in willingness to compete across genders, (`r unname(prop.table(t2)*100)[2]`%), `r apa_print(exploratory36, n = nrow(clean_fraud_removed))$statistic`. We discuss these findings about participants' beliefs in light of the actual study results in the discussion section. 


```{r, results = "asis"}


## print(ctable(practice$gender, practice$practice_problems_binary))
```


```{r, results = "asis"}
## print(ctable(clean$gender, clean$perc_gender_comp))
```



```{r, results = "asis"}
## print(ctable(clean$gender, clean$perc_gen_gender_pract))
```


