---
title: "results"
author: "Keana Richards"
date: "6/10/2020"
output:
  bookdown::word_document2:
  fig_caption: yes 
---

```{r, include = F}

## hiding code chunks globally 
knitr::opts_chunk$set(echo=F, message = F, warning = F)


## limiting number of digits to 2 decimal places
options(digits = 2)
options(repos="https://cran.rstudio.com" )
# load packages -----------------------------------------------------------


## Install devtools package if necessary
if(!"devtools" %in% rownames(installed.packages())) install.packages("devtools")


## Package names
packages <- c("readr", "tidyverse", "here", "devtools", "knitr", "officer", "summarytools")

## Install packages not yet installed
installed_packages <- packages %in% rownames(installed.packages())
if (any(installed_packages == FALSE)) {
  install.packages(packages[!installed_packages])
}

## Packages loading
invisible(lapply(packages, library, character.only = TRUE))

## Install the stable development versions from GitHub
if(!"papaja" %in% rownames(installed.packages())) devtools::install_github("crsh/papaja")



library(papaja)

source(here("study1", "source", "01_preregistered-analyses.R"))
source(here("study1", "source", "03_exploratory-analyses.R"))

```


```{r, results = "asis"}
## print(ctable(na_drop$gender, na_drop$condition))
```


Contrary to previous data in this literature [@Niederle2007], a minority of participants (`r freq(clean$comp_choice, report.nas = F)[6]`%) chose to compete. Despite the small proportion of participants who chose to compete, we still replicate the gender gap in the choice to compete when gender is included as the only predictor in the model, where a greater share of men (`r ctable(clean$gender, clean$comp_choice, useNA = "no")$proportions[4]*100`%) compared to women (`r ctable(clean$gender, clean$comp_choice, useNA ="no")$proportions[5]*100`%) chose to compete. A logistic regression revealed that this gender difference in the choice to compete is significant, `r apa_print(sec_exploratory6)$full_result$genderWoman`. However, when including control variables, such as risk attitudes, confidence, task scores, and the hypothesized interaction between gender and condition, we find that the effect of gender is no longer significant, `r apa_print(sec_exploratory11)$full_result$genderWoman`, while risk attitudes, `r apa_print(sec_exploratory11)$full_result$risk`, confidence, `r apa_print(sec_exploratory11)$full_result$conf_rank`, and task scores, `r apa_print(sec_exploratory11)$full_result$task_score`, are significant, suggesting those variables may fully explain the observed gender difference in willingness to compete. 

We observed gender differences in both risk attitudes, `r apa_print(sec_exploratory7)$full_result$genderWoman`, and confidence, `r apa_print(sec_exploratory8)$full_result$genderWoman`, in alignment with previous literature (CITES). When included as the sole predictor in a linear regression, we find that gender significantly predicts task scores on the paid multiplication task, `r apa_print(sec_exploratory9)$full_result$genderWoman`, such that women have lower scores on average, Mwomen=`r printnum(mean(women$task_score, na.rm = T))`, SD=`r printnum(sd(women$task_score, na.rm = T))`; Mmen= `r printnum(mean(men$task_score, na.rm = T))`, SD =`r printnum(sd(men$task_score, na.rm = T))`, `r apa_print(sec_exploratory12)$full_result$genderWoman`, which holds in a separate linear regression with other variables included as predictors in the model, `r apa_print(sec_exploratory12)$full_result$genderWoman`. 

Contrary to our predictions, we do not find evidence of a significant interaction between gender and condition on the decision to compete, `r apa_print(primary_hyp1)$full_result$conditionpract_genderWoman` (see Figure \@ref(fig:s100)). When included as a solo predictor of the choice to compete in a logistic regression, we did not find evidence that assignment to the knowledge of preparation affected the choice to compete, `r apa_print(sec_exploratory15)$full_result$conditionpract`. 

```{r, results = "asis"}
## print(stby(list(clean$gender, clean$condition), INDICES = clean$comp_choice, FUN = ctable))
```

As hypothesized, a logistic regression with gender predicting the choice to practice shows that a greater proportion of women (`r ctable(clean$gender, clean$pract_choice, useNA = "no")$proportions[5]*100`%) took advantage of the opportunity to practice relative to men (`r ctable(clean$gender, clean$pract_choice, useNA = "no")$proportions[4]*100`%), `r apa_print(sec_exploratory17)$full_result$genderWoman` (see Figure \@ref(fig:s107)). We replicate this effect after adding participants' choice to compete and the interaction between gender and the choice to compete in the model, `r apa_print(sec_exploratory2)$full_result$genderWoman`, but do not find an interaction between gender and the choice to compete, `r apa_print(sec_exploratory2)$full_result$full_result$genderWoman_comp_choicetournament` (see Figure \@ref(fig:s101)). We also find that the choice to compete positively predicts a participants' likelihood of choosing to practice, `r apa_print(sec_exploratory2)$full_result$comp_choicetournament`. In a subsequent logistic regression with additional possible predictors of the decision to practice, we find that the gender effect holds, `r apa_print(sec_exploratory14)$full_result$genderWoman`, suggesting that it is not explained by the observed gender differences in risk attitudes, confidence, nor task scores.^[Note: We also ran a two-part hurdle model with gender, competition choice, and the interaction between those variables predicting the number of practice rounds variable with the assumption that there may be different decision-making processes underlying the choice to prepare when first offered the opportunity versus the choice to continue preparing thereafter. However, we do not find evidence of gender differences in the choice to continue preparing after the initial decision to prepare - that is, the gender predictor in the count part of the model did not show a significant effect on the dependent variable].   

```{r t1, results = "asis"}
## print(stby(list(clean$gender, clean$comp_choice), INDICES = clean$pract_choice, FUN = ctable))

```

This gender difference in preparation aligned with participants' incentivized predictions about gender differences in preparation, where a greater proportion of participants (`r unname(prop.table(t15)*100)[2]`%) expected women, relative to the proportion that expected men (`r unname(prop.table(t15)*100)[1]`%), to spend more time preparing for the multiplication task, `r apa_print(exploratory7d, n= nrow(clean))$statistic` (see Figure \@ref(fig:s103)). They also expected women to prepare more in general, `r apa_print(exploratory7c, n = nrow(clean))$statistic`, with `r unname(prop.table(t14)*100)[2]`% indicating women prepare more in general and `r unname(prop.table(t14)*100)[1]`% indicating men prepare more in general (see Figure \@ref(fig:s106)). However, participants did not expect any gender differences in performance on the task, `r apa_print(exploratory7a, n = nrow(clean))$statistic` (see Figure \@ref(fig:s104)). Additionally, participants accurately predicted that women were less likely to choose to compete, `r apa_print(exploratory7b, n = nrow(clean))$statistic` (see Figure \@ref(fig:s105)). 

Finally, we analyzed participants responses to the questions about their calculator use and thoughts on using a calculator for the multiplication task. `r round(prop.table(table(clean$calc1))[2]*100, digits =0)`% of participants indicated that they thought using a calculator to answer the multiplication questions would slow them down and `r round(prop.table(table(clean$calc2))[1]*100, digits =0)`% of participants said they did not use a calculator. Importantly, there were no gender differences in perceptions of how calculators would affect performance, `r apa_print(exploratory5a, n = nrow(clean))$statistic`. Additionally, we did not find evidence of gender differences in actual calculator use, `r apa_print(exploratory5b, n = nrow(clean))$statistic`. 

```{r, results = "asis"}
## print(ctable(clean$gender, clean$perc_task_gender_pract))
```

```{r, results = "asis"}
## print(ctable(clean$gender, clean$better_gender_guess))
```

```{r, results = "asis"}
## print(ctable(clean$gender, clean$perc_gender_comp))
```

```{r, results = "asis"}
##print(ctable(clean$gender, clean$perc_gen_gender_pract))
```


