---
title: "results"
author: "Keana Richards"
date: "6/10/2020"
output:
  bookdown::word_document2:
  fig_caption: yes 
---

```{r, include = F}

## hiding code chunks globally 
knitr::opts_chunk$set(echo=F, message = F, warning = F)


## limiting number of digits to 2 decimal places
options(digits = 2)
options(repos="https://cran.rstudio.com" )
# load packages -----------------------------------------------------------


## Install devtools package if necessary
if(!"devtools" %in% rownames(installed.packages())) install.packages("devtools")


## Package names
packages <- c("readr", "tidyverse", "here", "devtools", "knitr", "officer", "summarytools")

## Install packages not yet installed
installed_packages <- packages %in% rownames(installed.packages())
if (any(installed_packages == FALSE)) {
  install.packages(packages[!installed_packages])
}

## Packages loading
invisible(lapply(packages, library, character.only = TRUE))

## Install the stable development versions from GitHub
if(!"papaja" %in% rownames(installed.packages())) devtools::install_github("crsh/papaja")

library(papaja)

source(here("study5", "source", "01_preregistered-analyses.R"))
source(here("study5", "source", "03_exploratory-analyses.R"))


na_drop <- clean %>% drop_na(condition) 

```

An equal number of participants were assigned to both conditions (control= `r freq(na_drop$condition)[5]`%). Of the males who completed the study, `r ctable(na_drop$gender, na_drop$condition)$proportions[1]*100`% were assigned to the control condition and of the females who completed the study, `r ctable(na_drop$gender, na_drop$condition)$proportions[2]*100`% were assigned to the control condition. 

```{r, results = "asis"}
## print(ctable(na_drop$gender, na_drop$condition))
```


We replicated the effect of gender on the choice to compete: `r ctable(clean$gender, clean$comp_choice)$proportions[4]*100`% of men chose to compete compared to `r ctable(clean$gender, clean$comp_choice)$proportions[5]*100`% of women. However, we do not find evidence of a significant effect of condition on the choice to compete among women, *z* = `r primary_hypothesis1_z`, *p* = `r primary_hypothesis1_pval` (see Figure \@ref(fig:s200)), contrary to our hypotheses. 

```{r, results = "asis"}
woman <- clean %>% filter(gender == "Woman")
## print(ctable(woman$comp_choice, woman$condition))

```

Despite no evidence for the effect of condition on the choice to compete among women, we replicate the effects found in Study 1, where women were significantly more likely to prepare for the task, even after being forced to prepare in the preparation condition (see Figure \@ref(fig:s204)). Women were `r (exp(coef(sec_exploratory1))[2] - 1)*100`% more likely to take advantage of the opportunity to prepare relative to men `r apa_print(exploratory1)$full_result$genderWoman`, while controlling for the decision to compete (see Figure \@ref(fig:s204)). Again, we find that these results align with participants' expectations, where they were significantly more likely to expect women to choose to prepare in general, `r apa_print(exploratory3c, n = nrow(clean))$statistic` (see Figure \@ref(fig:s203)), despite expecting men to choose to compete more often, `r apa_print(exploratory3b, n = nrow(clean))$statistic` (see Figure \@ref(fig:s202)) and expecting no gender differences in performance on the task, `r apa_print(exploratory3a, n = nrow(clean))$statistic` (see Figure \@ref(fig:s201)). 

```{r, results = "asis"}
## print(ctable(clean$gender, clean$better_gender_guess))
```


```{r, results = "asis"}
## print(ctable(clean$gender, clean$perc_gender_comp))
```



```{r, results = "asis"}
## print(ctable(clean$gender, clean$perc_gen_gender_pract))
```


